Pre-Main-Sequence M-Dwarfs With Complex Quasiperiodic Variability From Four Years of TESS

### 2023-06-14 paper/ms.tex
update ms

@@

%%%%%%%%
% CQVS %
%%%%%%%%
% dip-counting pipeline
\newcommand{\nuniqdipflagged}{{368}} % up-to-date; get_lgb_list_count.py
\newcommand{\ncpvsfound}{{48}}
\newcommand{\nmaybes}{{19}}

@@

% 250 word max!
\begin{abstract}
  Complex quasiperiodic variables (CQVs) are pre-main-sequence
  M-dwarfs with almost-periodic optical modulation that includes both
  sharp and broad troughs.  The troughs are usually superposed over
  smooth, spot-like modulation.  These objects are typically
  10-100\,million years old, and they do not seem to have primordial gas-rich
  disks.  Nonetheless, the preferred explanations for their optical
  variability invoke long-lived material in orbit at the corotation
  radius, for instance transiting dust clumps or stellar prominences.
  Here, we report new CQVs discovered in TESS data collected between
  July~2018 and Sep~2022.  Our search used two methods, the first
  based on counting dips in phase-folded light curves, and the second
  based on counting peaks in the Fourier domain.  From our analysis of
  \nstarssearched\ M-dwarfs with $T$$<$16 and $d$$<$150\,pc, we find
  \ncpvsfound\ gold-standard CQVs.  Most of these discoveries are new,
  and they include the brightest ($T$$\approx$10) and closest
  ($d$$\approx$20\,pc) examples of this class of object known.  A few
  objects are ``outliers among outliers''; for instance LP 12-502
  shows four to eight local minima per cycle distributed over a ``dip
  complex'' with a total duration that is nearly fixed over more than
  1000 cycles.  Nonetheless, LP-502 at times shows drastic shape
  changes over less than one cycle.  More generally, we find that none
  of the CQVs maintain a fixed light curve shape over timescales of
  more than a few hundred cycles -- hence, {\it quasi}periodic.
  Although the physical explanation behind these objects remains
  enigmatic, our sample may help clarify their origin.  Connections to
  star, disk, and exoplanet evolution are emphasized.
\end{abstract}

@@

Data from K2 and TESS have yielded a new class of variable star whose
root cause is not yet qualitatively understood: complex quasiperiodic
variables (CQVs).  These objects are identified phenomenologically
using their optical light curves, which show quasiperiodic troughs
that can be either sharp or broad, often superposed on smooth
spot-like modulation.  Some of the objects show up to eight local
minima (dips) per cycle; sharp peaks are also common.  Most of these
variable stars turn out to be pre-main-sequence M-dwarfs without
near-infrared excesses, with ages of $\approx$5-150 million years
(Myr), and rotation periods of at most two days; they are observed to
be $\approx$1\% of M-dwarfs younger than 100 Myr
\citep{2017AJ....153..152S,2018AJ....155...63S,2019ApJ...876..127Z,2022AJ....163..144G}.
The dips can be chromatic, with a reddening law plausibly consistent
with dust
\citep{2020AJ....160...86B,2022AJ....163..144G,2023MNRAS.518.2921K}.
And finally, while the dip shapes can ``jump'' between different
depths and durations over less than one cycle, they more often evolve
gradually, over tens to hundreds of cycles
\citep[e.g.][]{2017AJ....153..152S,2022ApJ...925...75P,2023ApJ...945..114P}.

The issue of what exactly causes the variability that defines the CQVs
has yet to be resolved.  There are a few competing explanations.  All
young M-dwarfs are spotted, which produces flux variations over
characteristic timescales of the rotation period, $P_{\rm rot}$, and
its half-harmonic, $0.5\,P_{\rm rot}$.  The observed dips occur over
durations as short as $0.05\,P_{\rm rot}$; a ``starspot-only''
scenario is therefore highly unlikely for any of the objects with
sufficiently sharp dips
\citep{2017AJ....153..152S,2021MNRAS.500.1366K}.   The more likely
scenarios instead invoke sharp geometries with material extrinsic to
the stellar surface \citep[see
Refs.~][]{2017AJ....153..152S,2022AJ....163..144G}.  In the ``clump''
scenario, opaque dust clumps orbiting near the Keplerian corotation
radius eclipse the star
\citep{2017AJ....153..152S,2023MNRAS.518.4734S}.  In the
``prominence'' scenario, long-lived condensations of plasma are
trapped along the star’s magnetic field lines, also near corotation
\citep{2022MNRAS.514.5465W}.  And in a ``screen'' scenario, the inner
wall of a quiescent circumstellar disk blocks a portion of the stellar
surface to produce sudden dips whenever spots come into view
\citep{2019ApJ...876..127Z}.  In our view, the arguments seem best
established for the dust clump and prominence hypotheses
\citep{2023MNRAS.518.4734S,2022MNRAS.514.5465W}.  However, unambiguous
evidence has yet to be presented to demonstrate which, if any, of
these scenarios is correct.

It has not yet been possible to rule between the candidate mechanisms
CQVs have historically been both hard to discover and hard to
characterize.   Discoverability has been linked to rarity: CQVs
comprise about 1\% of the youngest 1\% of M-dwarfs
\citep{2018AJ....155..196R}.  Out of the millions of stars monitored
by K2 and TESS, about 50 CQVs have been reported to date
\citep{2017AJ....153..152S,2018AJ....155...63S,2019ApJ...876..127Z,2022AJ....163..144G,2023ApJ...945..114P}.
The known CQVs are correspondingly faint; the initial K2 discoveries
\citep{2017AJ....153..152S} were M2-M6 dwarfs at distances
$\gtrsim$100\,pc, yielding optical brightnesses of $V$$\approx$15.5 to
$V$$>$20.  This renders time-series optical spectroscopy at high
resolution technically impossible, despite its potential utility in
ruling between the models.

@@

We analyzed the ``short'' 120-second cadence data
acquired by TESS between July~2018 and Sep~2022 (Sectors 1-55).
Specifically, we used the 120-second cadence light curve products
produced by the mission's Science Processing and Operations Center at
NASA Ames \citep{2016SPIE.9913E..3EJ}.  While the TESS data products
also include full frame images with cadences of 200, 600, and 1800
seconds, we limited our scope in this work for the sake of simplicity
in data handling.  In exchange, we lose out in both completeness and
homogeneity of the selection function.  While TESS cumulatively
observed $\approx$90\% of the sky for at least one lunar month between
July~2018 and Sep~2022, the 120-second cadence data were acquired for
only a pre-selected set of stars over Sectors 1-26, and then a
guest-investigator driven set of stars over Sectors 27-55
\citep{2021PASP..133i5002F}.

To assess the completeness of the resulting 120-second cadence data
that we analyze, we cross-matched TIC8 \citep{2018AJ....156..102S}
against the Gaia DR2 point-source catalog \citep{2018A&A...616A...1G}.
We opted for Gaia DR2 rather than DR3 because the base catalog for
TIC8 was Gaia DR2, which facilitated a one-to-one crossmatch using the
Gaia source identifiers.  This exercise showed that for $T$$<$16
M-dwarfs, the TESS 2-minute data are roughly 50\% complete at
$\approx$50\,pc.  At $<$20\,pc, $\gtrsim$80\% of the $T$$<$16 M-dwarfs
have at least one sector of short-cadence data; at $>$100\,pc,
$\lesssim$10\% of such M-dwarfs have at least one sector of
short-cadence data.  Armed with this understanding, we then used our
cross-match between Gaia DR2 and TIC8 to select our stars of interest,
which we defined as stars with 120-second cadence TESS light curves
that satisfied
\begin{align}
  T &< 16\\
  G_{\rm BP} - G_{\rm RP} &> 1.5 \\
  M_{\rm G} &> 4 \\
  d &< 150\,{\rm pc},
\end{align}
for $M_{\rm G} = G + 5\log(\varpi_{\rm as}) + 5$ the Gaia $G$-band
absolute magnitude, $\varpi_{\rm as}$ the parallax in units of
arcseconds, and a geometric distance $d$ defined by inverting the
parallax and ignoring any zero-point correction.  This selection
function includes dwarf stars later than spectral types of
$\approx$K6V.  This target sample includes \nstarssearched\ stars with
approximately M-dwarf spectral type, down to $T$$<$16 and out to
$d$$<$150\,pc.

@@

Previous methods that have yielded CQV discoveries include visually
examining stars known to be in young clusters
\citep{2017AJ....153..152S}, and automatically flagging rapid rotators
with a large number of strong Fourier harmonics
\citep{2019ApJ...876..127Z}.  The latter approach requires visual
vetting, since most rapid rotators with many Fourier harmonics are
false positives such as eclipsing binaries or multiple stars blended
into a single photometric aperture.  In this work, we implemented a
new search approach based on counting the number of sharp local minima
in phase-folded light curves, while also using the previously tested
Fourier approach.  We applied these two search techniques
independently.

@@

Broadly speaking, the most common false positives for both the Fourier
and dip-counting techniques were eclipsing binaries, spot-induced
variability from rapid rotators, and variability from neighboring,
off-target stars.  Typical false postive rates from our dip-counting
pipeline were 5:1, with 368 unique stars flagged, and about 20\% being
labelled either ``good'' or ``possible'' CQVs; for the Fourier
pipeline, {\bf the rate was X:Y, with ZZZZ unique stars flagged, and
NN\% being labelled ``good'' or ``possible'' CQVs}.

@@

\paragraph{Ages}
%TODO

@@

Table~\ref{tab:thetable} lists the \ncpvsfound\ CQVs identified by
our search, and some of their important properties.
The mosaic in Figure~\ref{fig:singlemosaic} shows the 40 brightest
objects.

For the TESS sectors in which these objects were identified, they show
anywhere from one to eight local minima per cycle.
Some stars show relatively ordinary modulation during one continuous
portion of the phased light curve, and highly structured modulation in
the remainder of the cycle (e.g. TIC~206544316, TIC~224283342,
TIC~402980664).
Others show structured modulation over the entire span of a cycle
(e.g. TIC~2234692, TIC~401789285, TIC~425933644, TIC~142173958).
Others still show some mix between these two modes,
with one or more small dips, superposed over one or more large dips.

@@

\begin{figure*}[!t]
	\begin{center}
    \centering
    \includegraphics[width=0.9\textwidth]{TIC_402980664_P18.5604_2min_phase_timegroups_mosaic.pdf}
		\vspace{-0.45cm}
		\caption{
			{\it Bottom:}
      Evolution of LP 12-502 ($P$=18.5604\,h) at fixed period over three
      years; small text denotes cycle number.  The TESS pointing law
      dictates time gaps; larger gaps tend to yield larger shape
      changes.
      The dips usually evolve over tens to hundreds of cycles.
      However cycles 1233-1264 show a dip that ``switched'' from a depth
      and duration of 3\% and 3\,hr to 0.3\% and 1\,hr over less than
      one cycle.
			\vspace{-0.8cm}
		}
		\label{fig:lp}
	\end{center}
\end{figure*}

@@

{\it Each CQV a snowflake}
One intriguing aspect of staring at Figure~\ref{fig:singlemosaic}
is that, even after rescaling the amplitudes, no two CQVs
exhibit exactly identical light curve morphology.
There are of course similarities.

TIC 272248916 and TIC 442571495

%A number of auxiliary
%questions follow.  After correcting for line-of-sight inclination, are
%most young M-dwarfs CQVs?  What observational signatures distinguish
%the proposed models (Figure~\ref{fig:f1}, bottom row)?  What
%organizational regularities characterize the CQV as a class of
%variable star?  What sets the extremes of the CQV population, such as
%the longest rotation periods, hottest stellar temperatures, and oldest
%stellar ages?  And finally, what connections, if any, do CQVs have to
%topics such as stellar evolution, M-dwarf magnetic fields, debris
%disks, and close-in exoplanets?

{\it Why would the prominence scenario tend toward corotation?}
This is analogous to quiescent
prominences on the Sun \citep{1967SoPh....2...39K}.

@@

@@

{\bf author contribution statement goes here}
L.G.B.~and R.~J. conceived the project and executed the
dip-based and Fourier-based searches, respectively.
They both drafted the initial manuscript.
S.~R. vetted the results from the Fourier search.
rotation- and lithium-based age analyses, and drafted the manuscript.
L.A.H.~contributed to project execution.
All authors assisted in manuscript revision.

@@

>>>>

\newcommand{\bprp}{G_{\rm BP} - G_{\rm RP}}

@@

%%%%%%%%
% CQVS %
%%%%%%%%
% dip-counting pipeline
\newcommand{\nuniqdipflagged}{{368}} % up-to-date; get_lgb_list_count.py

\input{vals_cqv_table_statistics}

@@

% 250 word max!
\begin{abstract}
  Complex quasiperiodic variables (CQVs) are pre-main-sequence
  M-dwarfs with almost-periodic optical modulation that includes both
  sharp and broad troughs.  The troughs are usually superposed over
  smooth, spot-like modulation.  These objects are typically
  10-100 million years (Myr) old, and they do not seem to have primordial gas-rich
  disks.  Nonetheless, the preferred explanations for their optical
  variability invoke long-lived material in orbit at the corotation
  radius, for instance transiting dust clumps or stellar prominences.
  Here, we report new CQVs discovered in TESS data collected between
  July~2018 and Sep~2022.  Our search used two methods, the first
  based on counting dips in phase-folded light curves, and the second
  based on counting peaks in the Fourier domain.  From our analysis of
  \nstarssearched\ M-dwarfs with $T$$<$16 and $d$$<$150\,pc, we find
  \ngoods\ gold-standard CQVs.  Most of these discoveries are new,
  and they include the brightest and closest
  examples of this class of object known ($T$$\approx$10; $d$$\approx$20\,pc).  A few
  objects are outliers among outliers; LP 12-502 for instance
  shows four to eight local minima per cycle distributed over a ``dip
  complex'' with a total duration that is nearly fixed over more than
  1000 cycles.  Nonetheless, LP-502 at times also showed drastic shape
  changes over less than one cycle.  More generally, we find that none
  of the CQVs maintain a fixed light curve shape over timescales of
  more than a few hundred cycles -- they are {\it quasi}periodic.
  Although the physical explanation behind these objects remains
  enigmatic, our sample may help clarify their origin.  Connections to
  star, disk, and exoplanet evolution are emphasized.
\end{abstract}

@@

Data from K2 and TESS have yielded a new class of variable star whose
root cause is not yet qualitatively understood: complex quasiperiodic
variables (CQVs).  Figure~\ref{fig:f1} shows a few examples.  These objects are identified phenomenologically
using their optical light curves, which show quasiperiodic troughs
that can be either sharp or broad, often superposed on smooth
spot-like modulation.  Some of the objects show up to eight local
minima (dips) per cycle; sharp peaks are also common.  Most of these
variable stars turn out to be pre-main-sequence M-dwarfs without
near-infrared excesses, with ages of $\approx$5-150 million years
(Myr), and rotation periods of at most two days; they are observed to
be $\approx$1\% of M-dwarfs younger than 100 Myr
\citep{2016AJ....152..114R,2017AJ....153..152S,2018AJ....155...63S,2019ApJ...876..127Z,2022AJ....163..144G}.
The dips can be chromatic, with a reddening law plausibly consistent
with dust
\citep{2020AJ....160...86B,2022AJ....163..144G,2023MNRAS.518.2921K}.
And finally, while the dip shapes can ``jump'' between different
depths and durations over less than one cycle, they more often evolve
gradually, over tens to hundreds of cycles
\citep[e.g.][]{2017AJ....153..152S,2022ApJ...925...75P,2023ApJ...945..114P}.

The issue of what exactly causes the variability that defines the CQVs
has yet to be resolved.  There are a few competing explanations.  All
young M-dwarfs are spotted, which produces flux variations over
characteristic timescales of the rotation period, $P_{\rm rot}$, and
its half-harmonic, $0.5\,P_{\rm rot}$.  The observed dips occur over
durations as short as $0.05\,P_{\rm rot}$; a ``starspot-only''
scenario is therefore highly unlikely for any of the objects with
sufficiently sharp dips
\citep{2017AJ....153..152S,2021MNRAS.500.1366K}.   The more likely
scenarios instead invoke sharp geometries with material extrinsic to
the stellar surface \citep[e.g.][]{2017AJ....153..152S,2022AJ....163..144G}.  In the ``clump''
scenario, opaque dust clumps orbiting near the Keplerian corotation
radius eclipse the star
\citep{2017AJ....153..152S,2023MNRAS.518.4734S}.  In the
``prominence'' scenario, long-lived condensations of plasma are
trapped along the star’s magnetic field lines, also near corotation
\citep{2022MNRAS.514.5465W}.  And in a ``screen'' scenario, the inner
wall of a quiescent circumstellar disk blocks a portion of the stellar
surface to produce sudden dips whenever spots come into view
\citep{2019ApJ...876..127Z}.  In our view, the arguments seem best
established for the dust clump and prominence hypotheses
\citep{2023MNRAS.518.4734S,2022MNRAS.514.5465W}.  However, unambiguous
evidence has yet to be presented to demonstrate which, if any, of
these scenarios is correct.

It has not yet been possible to rule between the candidate mechanisms
CQVs have historically been both hard to discover and hard to
characterize.   Discoverability has been linked to rarity: CQVs
comprise about 1\% of the youngest 1\% of M-dwarfs
\citep{2018AJ....155..196R}.  Out of the millions of stars monitored
by K2 and TESS, about 50 CQVs have been reported to date
\citep{2016AJ....152..114R,2017AJ....153..152S,2018AJ....155...63S,2019ApJ...876..127Z,2020AJ....160...86B,2022AJ....163..144G,2023ApJ...945..114P}.
The known CQVs are correspondingly faint; the initial K2 discoveries
\citep{2016AJ....152..114R,2017AJ....153..152S} were M2-M6 dwarfs at distances
$\gtrsim$100\,pc, yielding optical brightnesses of $V$$\approx$15.5 to
$V$$>$20.  This renders time-series optical spectroscopy at high
resolution technically impossible, despite its potential utility in
ruling between the models.

@@

We analyzed the ``short'' 120-second cadence data
acquired by TESS between July~2018 and Sep~2022 (Sectors 1-55).
Specifically, we used the 120-second cadence light curve products
produced by the mission's Science Processing and Operations Center at
NASA Ames \citep{2016SPIE.9913E..3EJ}.  While the TESS data products
also include full frame images with cadences of 200, 600, and 1800
seconds, we limited our scope in this work for the sake of simplicity
in data handling.  In exchange, we lose in both completeness and
homogeneity of the selection function.  While TESS cumulatively
observed $\approx$90\% of the sky for at least one lunar month between
July~2018 and Sep~2022, the 120-second cadence data were acquired for
only a pre-selected set of stars over Sectors 1-26, and then a
guest-investigator driven set of stars over Sectors 27-55
\citep{2021PASP..133i5002F}.

To assess the completeness of the resulting 120-second cadence data
that we analyze, we cross-matched TIC8 \citep{2018AJ....156..102S}
against the Gaia DR2 point-source catalog \citep{2018A&A...616A...1G}.
We opted for Gaia DR2 rather than DR3 because the base catalog for
TIC8 was Gaia DR2, which facilitated a one-to-one crossmatch using the
Gaia source identifiers.  This exercise showed that for $T$$<$16
M-dwarfs, the TESS 2-minute data are roughly 50\% complete at
$\approx$50\,pc.  At $<$20\,pc, $\gtrsim$80\% of the $T$$<$16 M-dwarfs
have at least one sector of short-cadence data; at $>$100\,pc,
$\lesssim$10\% of such M-dwarfs have at least one sector of
short-cadence data.  Armed with this understanding, we then used our
cross-match between Gaia DR2 and TIC8 to select our stars of interest,
which we defined as stars with 120-second cadence TESS light curves
that satisfied
\begin{align}
  T &< 16 \quad&(\mathrm{Bright\ for\ TESS})\\
  \bprp &> 1.5 \quad&(\mathrm{Red\ stars\ only}) \\
  M_{\rm G} &> 4 \quad&(\mathrm{Dwarf\ stars\ only})  \\
  d &< 150\,{\rm pc} \quad&(\mathrm{Close\ stars\ only}),
\end{align}
for $M_{\rm G} = G + 5\log(\varpi_{\rm as}) + 5$ the Gaia $G$-band
absolute magnitude, $\varpi_{\rm as}$ the parallax in units of
arcseconds, and a geometric distance $d$ defined by inverting the
parallax and ignoring any zero-point correction.  This selection
function includes dwarf stars later than spectral types of
$\approx$K6V.  This target sample includes \nstarssearched\ stars with
approximately M-dwarf spectral type, down to $T$$<$16 and out to
$d$$<$150\,pc.

@@

Previous methods that have yielded CQV discoveries include visually
examining stars known to be in young clusters
\citep{2016AJ....152..114R,2017AJ....153..152S}, and automatically flagging rapid rotators
with a large number of strong Fourier harmonics
\citep{2019ApJ...876..127Z}.  The latter approach requires visual
vetting, since most rapid rotators with many Fourier harmonics are
false positives such as eclipsing binaries or multiple stars blended
into a single photometric aperture.  In this work, we implemented a
new search approach based on counting the number of sharp local minima
in phase-folded light curves, while also using the previously tested
Fourier approach.  We applied these two search techniques
independently.

@@

Broadly speaking, the most common false positives for both the Fourier
and dip-counting techniques were eclipsing binaries, spot-induced
variability from rapid rotators, and variability from neighboring,
off-target stars.  Typical false postive rates from our dip-counting
pipeline were 5:1, with \nuniqdipflagged\ unique stars flagged, and about 20\% being
labelled either ``good'' or ``possible'' CQVs; for the Fourier
pipeline, {\bf the rate was X:Y, with ZZZZ unique stars flagged, and
NN\% being labelled ``good'' or ``possible'' CQVs}.

@@

\paragraph{Ages}
We estimated the stellar ages by making probabilistic spatial and
kinematic associations between the CQVs and known clusters in the solar
neighborhood.  For most of the stars in our sample, we were able to do
this using BANYAN\,$\Sigma$
\citep{2018ApJ...856...23G}.\footnote{\url{https://github.com/jgagneastro/banyan_sigma},
git commit \texttt{394b486}} This algorithm calculates the
probability that a given star belongs to one of 27 young
clusters (or ``assocations'') within 150\,pc of the Sun, by modeling the clusters
as multivariate Gaussians in 3-D position and 3-D velocity space.  
We used the
Gaia DR2 sky positions, proper motions, and distances to calculate the
membership probabilities.  
BANYAN\,$\Sigma$ in turn analytically marginalizes over the radial velocity dimension.
We emphasize that the probabilities returned by this procedure are qualitatively
useful, but quantitatively dubious due to the non-Gaussian
nature of most groups within the
solar neighborhood \citep[see e.g.][Figure~10]{2021ApJ...917...23K}.

For a few cases where BANYAN\,$\Sigma$
yielded ambiguous results, we consulted the meta-catalog of young,
age-dated, and age-dateable stars within a kiloparsec from
\citet{2022AJ....163..121B}, and also searched the local volume around
each star for co-moving
companions.\footnote{\url{https://github.com/adamkraus/Comove}, git commit \texttt{278b372}}

@@

Table~\ref{tab:thetable} lists the \ncpvsfound\ CQVs identified by
our search, and some of their important properties.
\ngoods\ objects demonstrate what we view as unambiguous
characteristics of the CPV phenomenon in at least one TESS sector, and
we refer to these as the ``gold sample''.
The remaining \nmaybes\ CPV candidates were ambiguous (in our view),
and their variability might be caused by say, multiple starspot
groups.

The mosaic in Figure~\ref{fig:singlemosaic} shows phased light curves
for the 40 brightest objects.
The TESS sectors in which these objects were identified show
anywhere from one to eight local minima per cycle.
Some stars show relatively ordinary modulation during one continuous
portion of the phased light curve, and highly structured modulation in
the remainder of the cycle (e.g. TIC~206544316, TIC~224283342,
TIC~402980664).
Others show structured modulation over the entire span of a cycle
(e.g. TIC~2234692, TIC~401789285, TIC~425933644, TIC~142173958).
Others still show some mix between these two modes.

\subsection{Ages}

Of our \ncpvsfound\ confirmed and candidate CQVs, \nnotfieldbanyan\ 
were confidently associated with a nearby moving group or open
cluster using BANYAN\,$\Sigma$.
The relevant groups are listed in Table~\ref{tab:thetable}; their ages
span $\approx$5-150\,Myr.
The most prodigious groups were Sco-Cen, Tuc-Hor, and Columba.
The yield of CQVs in Sco-Cen (LCC / UCL / USco) is not surprising,
since Sco-Cen contains the majority of pre-main-sequence stars in the
solar neighborhood.
The absence of CQVs in IC2602 and IC2391 is because those clusters are
beyond 100\,pc, where the completeness of the TESS 120-second cadence
data is below 10\%.

Of the the \ngoodsfieldbanyan\ non-associated stars, one
(TIC~302160226) is an obvious member of $\alpha$~Per ($t\approx
86\pm16$\,Myr; \citealt{2022arXiv221109822B}).  For the other two
(TIC~58084670 and TIC~141146667), we are convinced of both their CPV
status and their youth, but we were not able to confidently associate
either star with any young groups.
Both were noted as being in the ``diffuse'' Class~II YSO
population by \citet{2021ApJ...917...23K}.
That diffuse population may contain kinematic structures that have yet
to be unravelled, however the absence of obvious young, co-moving
stars within $\Delta r$=$40$\,pc and $\Delta v$=$3$\,km\,s$^{-1}$
of these stars suggest that they may have run away from their birth
locations.

The CQV phenomenon persists at least up to 150\,Myr.  Our catalog
includes three $\approx$150\,Myr old AB Dor members (TIC~288344202,
TIC~332517282, and TIC~368129164), a $\approx$112\,Myr old Pleiades
member (TIC~440725886; \citealt{CantatGaudin_2020}), and a
similarly-aged Psc-Eri member (TIC~38539720;
\citealt{2020A&A...639A..64R}).  To our best knowledge, TIC~332517282
was the previous record-holder for oldest-known CQV
\citep{2019ApJ...876..127Z,2022AJ....163..144G}; at least one
unambiguous case (EPIC~211070495) and a few other candidates were
also previously known in the Pleiades \citep{2016AJ....152..114R}.
While we expect to have been sensitive to CQVs in the nearby Hyades
($\approx$700\,Myr), 
again due to the specifics of the TESS 120-second selection function,
we do not know at this time whether we would have been sensitive to
such stars.

Finally, six CQVs were identified in the recently
confirmed Argus association \citep{2019ApJ...870...27Z}.
This serves as an indirect line of evidence supporting the reality,
and youth, of that group.

@@

\begin{figure*}[!t]
	\begin{center}
    \centering
    \includegraphics[width=0.9\textwidth]{TIC_402980664_P18.5604_2min_phase_timegroups_mosaic.pdf}
		\vspace{-0.45cm}
		\caption{
			{\it Bottom:}
      Evolution of LP 12-502 ($P$=18.5604\,h) at fixed period and epoch over three
      years; small text denotes cycle number.  The TESS pointing law
      dictates time gaps; larger gaps tend to yield larger shape
      changes.
      The dips usually evolve over tens to hundreds of cycles.
      However cycles 1233-1264 show a dip that ``switched'' from a depth
      and duration of 3\% and 3\,hr to 0.3\% and 1\,hr over less than
      one cycle.
		}
		\label{fig:lp}
	\end{center}
\end{figure*}

@@

\paragraph{Some CQVs require external occulters}
(rehash Bodman2017 timescale arguments)

\paragraph{Each CQV a snowflake?}
One intriguing aspect of staring at Figure~\ref{fig:singlemosaic}
is that, even after rescaling the amplitudes, no two CQVs
exhibit exactly identical light curve morphology.
There are of course similarities.

TIC 272248916 and TIC 442571495 match.

\paragraph{Predicting the future, given the past}
Figure~\ref{fig:evoln}
shows that for 21 CQVs that were observed roughly two years
apart, 5 showed obvious signs of the phenomenon in one sector,
and marginal or non-existence signs in the other.
We emphasize that the periods themselves were usually stable to $<$0.1\%.
However, this shape evolution
suggests that CQVs have a duty cycle of $\approx$75\%.

\paragraph{Why would the prominence scenario tend toward corotation?}
This is analogous to quiescent
prominences on the Sun \citep{1967SoPh....2...39K}.

@@

We report on the existence of \ngoods\ objects that showed bonafide
CQV behavior over at least one TESS sector between July~2018 and Sep~2022.
Our search for these objects was restricted to dwarf stars bright enough
for 1\% precision photometry with TESS over 1 hour ($T$$<$16),
that were red ($\bprp<1.5$) and within 150\,pc of the Sun.
We also note an additional \nmaybes\ candidate CQVs.

Analyzing the light curves of these objects, we can make the following conclusions.

\begin{itemize}
	%
	\item CQVs are {\it quasi}periodic.
	%
	\item The CQV phenomenon persists for at least 150\,Myr.
	%
	\item CQVs evolve over timescales that are both secular ($>$100\,cycles) and impulsive ($<$1 cycle).
	%
	\item The CQV duty cycle is $\approx 75$\%, based on 
	the fraction of bonafide CQVs that ``turned off'' during TESS re-observations.
\end{itemize}

Many questions remain.
After correcting for line-of-sight inclination, are
most young M-dwarfs CQVs?  What observational signatures distinguish
the proposed models (Figure~\ref{fig:f1}, bottom row)?  What
organizational regularities characterize the CQV as a class of
variable star?  What physically sets the extremes of the CQV population, such as
the longest rotation periods, hottest stellar temperatures, and oldest
stellar ages?  And finally, what connections, if any, do CQVs have to
topics such as stellar evolution, M-dwarf magnetic fields, debris
disks, and close-in exoplanets?
While we have tried to point out possible connections, the most
likely path toward definitive resolutions would be to observe a full
phase curve of LP 12-502 using JWST/MIRI.

@@

{\bf author contribution statement goes here}
L.G.B.~and R.~J. conceived the project and executed the
dip-based and Fourier-based searches, respectively.
They both drafted the initial manuscript.
L.G.B.~performed the cluster membership analysis.
S.~R. vetted the results from the Fourier search.
L.A.H.~contributed to project design.
All authors assisted in manuscript revision.

@@

\section{The LP 12-502 glitch}

Figure~\ref{fig:lpzoom} shows an alternative view of cycles 1233-1247
from Figure~\ref{fig:lp}.

\begin{figure*}[!t]
	\begin{center}
		\centering
		\includegraphics[width=0.96\textwidth]{TIC4029_zoom.png}
		\vspace{-0.45cm}
		\caption{
			LP 12-502 is wild.
		}
		\label{fig:lpzoom}
	\end{center}
\end{figure*}
